---
title: "Model runner API example"
output: html_document
date: '2022-05-26'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries

```{r}
library(jsonlite)
library(httr)
library(rlist)
```

## Set token/URL

```{r}
token <- Sys.getenv("API_TOKEN", NA)
stopifnot(!is.na(token))
url <- Sys.getenv("API_BASE_URL", "https://covid-modelling-stg.epcc.ed.ac.uk")
```



```{r}
model_slug <- "sir-ode-python"
headers <- c(
  "accept"="application/json; charset=utf-8", 
  "Content-Type"="application/json", 
  "Authorization"=paste("Bearer ",token)
)
```

## Input

```{r}
inputJSON <-  list(
  "p" = c(0.5,0.25),
  "u0" = c(0.99,0.01,0.0),
  "tspan" =  c(0,10000)
)
```


## Post simulations

```{r}
post_simulations_response = POST(url,
                                 path = c("api", "simulations", "model-runs", model_slug),
                                 body = toJSON(inputJSON, auto_unbox = TRUE),
                                 add_headers(.headers=headers))
stopifnot(post_simulations_response$status_code==200)
post_simulations_content <- content(post_simulations_response,as="parsed")
post_simulations_content
```
We need the ID to construct other URLs later.

```{r}
simulation_id=post_simulations_content$id
```

## Check that model call was successful

The model call should be successful if (a) a status code 200 is returned in the `POST` and (b) if the JSON conforms to the schema.

```{r}
check_simulations_response <- GET(url,
                                  path=c("api", "simulations", simulation_id, "model-runs", model_slug),
                                  add_headers(.headers=headers))
stopifnot(check_simulations_response$status_code==200)
check_simulations_content <- content(check_simulations_response,as="parsed")
check_simulations_content
```
The process can take some time to complete.
The following code polls the API to check for success every `step` seconds, with a `timeout` in seconds.

```{r}
stp <- 60
timeout <- 600

tm <- 0
while(tm <= timeout){
  check_simulations_response <- GET(url,
                                    path=c("api", "simulations", simulation_id, "model-runs", model_slug),
                                    add_headers(.headers=headers))
  stopifnot(check_simulations_response$status_code==200)
  check_simulations_content <- content(check_simulations_response,as="parsed")
  if(check_simulations_content$status=="complete"){
    break
  }
  Sys.sleep(stp)
  tm <- tm+stp
}

if(tm==timeout){
  print("API timed out")
}
```

```{r}
check_simulations_content
```

## Export simulation output

```{r}
export_simulations_response <- GET(url,
                                   path=c("api", "simulations", simulation_id, "model-runs", model_slug, "export"),
                                   add_headers(.headers=headers))
stopifnot(export_simulations_response$status_code==200)
export_simulations_content <- content(export_simulations_response,as="parsed")
export_simulations_content
```


